---
output: github_document
---

**This library mainly for cleaning antiobiotics data by leveraging AMR Package, with some additional useful functions.**

## Usages

```         
amrabxlookup::clean_antibiotics(
  x ,
 ... 
  )

amrabxlookup::check_previous_events(df, cols, sort_by_col, patient_id_col,
                                event_indi_value="R", new_col_prefix="pr_event_", 
                                time_period_in_days = 0, minimum_prev_events = 0)
  

amrabxlookup::transpose_microbioevents(df, key_columns, required_columns, transpose_key_column,
                                      transpose_value_column, fill = "N/A")                              
                                
```

<!-- df   A data frame containing microbiology events -->

<!-- cols  Columns for each antibiotics which contains events -->

<!-- sort_by_col  A date column to order the input data frame -->

<!-- patient_id_col  Patient Id Column -->

<!-- event_indi_value (optional)  Event value indicating Resistance (Default 'R' ) -->

<!-- new_col_prefix (optional)   Custom Prefix for new column(Default 'pr_event_' ) -->

<!-- time_period_in_days (optional)  Values to check any  previous events in last 'n' days or not -->

<!-- minimum_prev_events (optional)  Values to check any 'n' number of previous events happened or not -->

# amrabxlookup

<!-- badges: start -->

<!-- badges: end -->

The goal of amrabxlookup is to find matching antibiotics in AMR dataset and some other additinal useful utility functions.

## Installation

You can install the development version of amrabxlookup from [GitHub](https://github.com/) with:

``` r
install.packages("devtools")
devtools::install_github("CAMO-NET-LIV/amrabxlookup", auth_token="<your_personal_access_token>")

or

install.packages("pak")
pak::pak("CAMO-NET-LIV/amrabxlookup")

```

## Examples

This is a basic example which shows you how to solve a common problem:

```{r example}
library(amrabxlookup)
## basic example code
amrabxlookup::clean_antibiotics(c("Amoxicilli"))

```

```{r example2}
library(amrabxlookup)
## basic example code
df <- data.frame(drug = c("Amoxicilln","moxicillin","Paracetamol") )
amrabxlookup::clean_antibiotics(df, drug_col = drug)
```

```{r example3}
library(amrabxlookup)
## basic example code
df <- data.frame(subject_id=c('10016742','10016742','10016742','10016742','10016742','10038332','10038332','10038332','10038332','10038332','10038332'),
                          chartdate= c('2178-07-03','2178-08-01','2178-08-01','2178-08-01','2178-09-25','2164-07-31','2164-12-22','2164-12-22','2165-01-07','2165-04-17','2165-05-05'),
                          CEFEPIME=c('R','R','R','R','S','R','R','R','S','S','S'),
                          CEFTAZIDIME=c('S','R','S','R','R','S','S','S','R','R','S'))
    amrabxlookup::check_previous_events(df, cols = c('CEFTAZIDIME'), sort_by_col = 'chartdate', patient_id_col = 'subject_id', event_indi_value='R')
```

```{r example4}
## example with 'minimum_prev_events' parameter
 df <- data.frame(subject_id=c('10016742','10016742','10016742','10016742','10016742','10038332','10038332','10038332','10038332','10038332','10038332'),
                          chartdate= c('2178-07-03','2178-08-01','2178-07-22','2178-08-03','2178-09-25','2164-07-31','2164-12-22','2164-12-22','2165-01-07','2165-04-17','2165-05-05'),
                          CEFEPIME=c('R','S','R','S','S','R','R','R','S','S','S'),
                          CEFTAZIDIME=c('S','R','S','R','R','S','S','S','R','R','S'))
  amrabxlookup::check_previous_events(df, cols = c('CEFEPIME'), sort_by_col = 'chartdate', patient_id_col = 'subject_id', minimum_prev_events = 2)

```

```{r example5}
## example with 'time_period_in_days' parameter
df <- data.frame(subject_id=c('10016742','10016742','10016742','10016742','10016742','10038332','10038332','10038332','10038332','10038332','10038332'),
                          chartdate= c('2178-07-03','2178-08-01','2178-07-22','2178-08-03','2178-09-25','2164-07-31','2164-12-22','2164-12-22','2165-01-07','2165-04-17','2165-05-05'),
                          CEFEPIME=c('R','S','R','S','S','R','R','R','S','S','S'),
                          CEFTAZIDIME=c('S','R','S','R','R','S','S','S','R','R','S'))
amrabxlookup::check_previous_events(df, cols = c('CEFTAZIDIME'), sort_by_col = 'chartdate', patient_id_col = 'subject_id', time_period_in_days = 25)


```

```{r example6}
## example with 'time_period_in_days' & 'minimum_prev_events' parameters
df <- data.frame(subject_id=c('10016742','10016742','10016742','10016742','10016742','10038332','10038332','10038332','10038332','10038332','10038332'),
                          chartdate= c('2178-07-03','2178-08-01','2178-08-01','2178-08-01','2178-09-25','2164-07-31','2164-12-22','2164-12-22','2165-01-07','2165-04-17','2165-05-05'),
                          CEFEPIME=c('R','R','R','R','S','R','R','R','S','S','S'),
                          CEFTAZIDIME=c('S','R','S','R','R','S','S','S','R','R','S'))
                          
amrabxlookup::check_previous_events(df, cols = c('CEFEPIME'), sort_by_col = 'chartdate', patient_id_col = 'subject_id', time_period_in_days = 62, minimum_prev_events = 2)


```

```{r example7}
##example for transpose_microbioevents
test_data <- data.frame(subject_id=c('10016742','10016742','10016742','10016742','10016742','10038332','10038332','10038332','10038332','10038332','10038332'),
                          chartdate= c('2178-07-03','2178-08-01','2178-08-01','2178-08-01','2178-09-25','2164-07-31','2164-12-22','2164-12-22','2165-01-07','2165-04-17','2165-05-05'),
                          ab_name=c('CEFEPIME','CEFTAZIDIME','CEFEPIME','CEFEPIME','CEFTAZIDIME','CEFTAZIDIME','CEFEPIME','CEFEPIME','CEFTAZIDIME','CEFTAZIDIME','CEFEPIME'),
                          interpretation=c('S','R','S','R','R','S','S','S','R','R','S'))

amrabxlookup::transpose_microbioevents(test_data, key_columns = c('subject_id','chartdate','ab_name') , required_columns =c('subject_id','chartdate'), transpose_key_column = 'ab_name',
                                                    transpose_value_column = 'interpretation', fill = "N/A")
```
